### 2016-11-04 introduction.tex
more shit

In this work we propose and evaluate a novel algorithm for pruning whole neurons from a trained neural network without any re-training and examine its performance compared to simpler methods. We then analyze the kinds of errors made by our algorithm and use this to launch an investigation into the fundamental nature of learning representations in neural networks. We find that our results corroborate a seemingly forgotten 27-year old observation by \cite{mozer1989skeletonization} concerning the nature of neural network learning.

>>>>

In this work we propose and evaluate a novel algorithm for pruning whole neurons from a trained neural network without any re-training and examine its performance compared to simpler methods. We then analyze the kinds of errors made by our algorithm and use this to launch an investigation into the fundamental nature of learning representations in neural networks. We find that our results corroborate a seemingly forgotten 27-year old observation by \cite{mozer1989skeletonization} concerning the nature of neural network learning. This observation is best summarized in a quotation from \cite{segee1991fault} on the notion of fault-tolerance in multilayer perception networks:

\begin{quotation}
Contrary to the belief widely held, multilayer networks are \textit{not} inherently fault tolerant. In fact, the loss of a single weight is frequently sufficient to completely disrupt a learned function approximation. Furthermore, having a large number of weights \textit{does not seem} to improve fault tolerance. [Emphasis added]
\end{quotation}

Essentially, \cite{mozer1989using} observed that the behavior of neural networks during training is not to distribute the learning representation evenly or even equitably across hidden units. What actually happens is that a few, elite neurons learn an approximation of the input-output function, and the remaining units simply learn a complex interdependence function which cancels out their respective influence. This is evinced by the fact that in many cases, whole neurons can be removed from a network with minimal to no impact on the output approximation. In this sense, there are few bipartisan units in a trained network. A unit is typically either part of the input-output function approximation, or it is part of an elaborate noise cancellation task force. Assuming this is true, most of the compute-time spent training a neural network is likely occupied by this arguably wasteful procedure of silencing superfluous parameters, and pruning is thus part of a necessary treatment procedure to ``trim the fat''.

We observed this very same phenomenon in our experiments, and this is the motivation behind our decision to evaluate our algorithms on the criteria of their ability to trim neurons without any re-training. As \cite{fahlman1989cascade} discuss, the ``herd effect'' and ``moving target'' problems in back-propagation learning simply cause the remaining units in a network to shift course and What we discovered is that predicting the behavior of a network when a unit is to be pruned is very difficult, and
